### 2013-08-03 main.tex
minor fixes, images
fix bibliography
use natbib citation commands everywehere.
use garamond :)

\documentclass[12pt,toc=bibnumbered, a4paper,twoside]{scrreprt}

\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\renewcommand{\eqref}[1]{Equation~(\ref{#1})}
\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}

@@

\begin{document}

%\title{Learning a Loopy Model For Semantic Segmentation Exactly}

\begin{titlepage}
\begin{center}
\vspace*{1in}
\textbf{{\LARGE PhD Thesis}}
\par
\vspace{1.5in} {\large Andreas Mueller}
 \par \vfill A Thesis submitted for the degree of Doctor of Philosophy
\par \vspace{0.5in}
Department IV, Institute for Computer Science
\par \vspace{0.5in}
Friedrich-Willhelm Universitaet Bonn \par
\vspace{0.5in} September 2013 \end{center}

@@

\begin{abstract} abstract
\end{abstract}

@@

@@

\bibliography{main}
\end{document}

>>>>

\documentclass[12pt,toc=bibnumbered, a4paper,twoside]{scrbook}

\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{listings}
\usepackage[urw-garamond]{mathdesign}
\usepackage{garamondx}
%\usepackage{layout}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand{\x}{\checkmark}
\renewcommand{\o}{$\times$}
\newcommand{\pystruct}{{\sc PyStruct} }

\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}

\newtheorem{corollary}{Corollary}
\newtheorem{corollarya}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{theorema}{Theorem}

\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}{>{\centered\arraybackslash}X}

\newcommand{\fix}{\marginpar{FIX}} \newcommand{\new}{\marginpar{NEW}}
\newcommand\etal{~et\,al.~}

@@

\begin{document}
%\layout

\begin{titlepage}
\begin{center}
\vspace*{1in}
\textbf{{\LARGE Dissertation}}
\par
\vspace{1.5in} {\large Andreas M\"uller}
 \par \vfill A Thesis submitted for the degree of Doctor of Philosophy
\par \vspace{0.5in}
Institute for Computer Science \par
Department IV, Autonomous Intelligent Systems
\par \vspace{0.5in}
Friedrich-Willhelm Universit\"at Bonn \par
\vspace{0.5in} September 2013 \end{center}

@@

@@

\chapter{introduction}

@@

\chapter{Conclusion}

\bibliographystyle{plainnat}
\bibliography{main}
\end{document}
